---
title: "paper"
author: "Carlos A. Sierra"
date: "15 März 2017"
output: html_document
---

Abstract. Determining environmental controls on soil organic matter decomposition is of importance for developing models that predict the effects of environmental change on global soil carbon stocks. There is uncertainty about the environmental controls on decomposition rates at temperature and moisture extremes, particularly at high water content levels and high temperatures. It is uncertain whether observed declines in decomposition rates at high temperatures are due to declines in the heat capacity of extracellular enzymes as predicted by thermodynamic theory, or due to simultaneous declines in soil moisture. It is also uncertain whether oxygen limits decomposition rates at high water contents. Here we present the results of a full factorial experiment using organic soils from a boreal forest incubated at high temperatures (25 and 35 C), a wide range of water-filled pore space (WFPS; 15, 30, 60, 90 %), and contrasting oxygen concentrations (1 and 20 %). We found support for the hypothesis that decomposition rates are high at high temperatures, provided that enough moisture and oxygen are available for decomposition. Furthermore, we found that decomposition rates are
mostly limited by oxygen concentrations at high moisture levels; even at 90% WFPS, decomposition proceeded at high rates in the presence of oxygen. Our results suggest an important degree of interaction among temperature, moisture, and oxygen in determining decomposition rates at the soil core scale.

```{r include=FALSE}
###########################################################################################
##    Interactions among temperature, moisture, and oxygen concentrations in 
##                   controlling decomposition rates.
#     R code to reproduce all results
###########################################################################################
# Code by: Carlos A. Sierra
# csierra@bgc-jena.mpg.de
###########################################################################################

# Load required R packages
library(SoilR)
library(FME)

# Set working directory
#setwd("bg-2016-474-supplement") #set to location where you stored supplement files

#Read the data
IAll=read.csv("IncubationsAll.csv") #Data from all incubation columns
co2=read.csv("CO2incubations.csv") #Data aggregated by treatment
```

```{r}
# 1. Initial plots and comparison of treatment data

#Function to subset data from specific combinations of temperature, moisture, oxygen
subst=function(t,m,o){
  tmp1=subset(co2,Temperature==t)
  tmp2=subset(tmp1,Moisture==m)
  tmp3=subset(tmp2,Oxygen==o,select=c(Day,CO2efflux,sd))
  return(tmp3)
}

treatments=unique(co2[,4:6])

plotIncunation=function(trt,...){
  tmp=subst(t=as.numeric(trt[1]),m=as.numeric(trt[2]),o=as.numeric(trt[3]))
  plot(tmp[,1],cumsum(tmp[,2]),type="o",...)
}

linesIncunation=function(trt,...){
  tmp=subst(t=as.numeric(trt[1]),m=as.numeric(trt[2]),o=as.numeric(trt[3]))
  lines(tmp[,1],cumsum(tmp[,2]),type="o",...)
}

# Plot for answer to Reviewer 1
par(mfrow=c(2,2), mar=c(4.5,4.5,1,0.5))
plotIncunation(trt=c(25,15,1),ylim=c(0,1200), xlab="Incubation time (days)", ylab=expression(paste("Cummulative respired C (", mu,"g)")), main="Low oxygen (1%)")
linesIncunation(trt=c(25,30,1),col=2)
linesIncunation(trt=c(25,60,1),col=3)
linesIncunation(trt=c(25,90,1),col=4)
legend("topright",c("WFPS:","15 %", "30 %", "60 %", "90 %"), col=0:4,lty=1,bty="n")
legend("topleft",expression(paste("Temperature: 25", degree,"C")), bty="n")

plotIncunation(trt=c(25,15,20),ylim=c(0,1200), xlab="Incubation time (days)", ylab="", main="High oxygen (20%)")
linesIncunation(trt=c(25,30,20),col=2)
linesIncunation(trt=c(25,60,20),col=3)
linesIncunation(trt=c(25,90,20),col=4)
legend("topright",c("WFPS:","15 %", "30 %", "60 %", "90 %"), col=0:4,lty=1,bty="n")
legend("topleft",expression(paste("Temperature: 25", degree,"C")), bty="n")

plotIncunation(trt=c(35,15,1),ylim=c(0,1200), xlab="Incubation time (days)", ylab=expression(paste("Cummulative respired C (", mu,"g)")))
linesIncunation(trt=c(35,30,1),col=2)
linesIncunation(trt=c(35,60,1),col=3)
linesIncunation(trt=c(35,90,1),col=4)
legend("topright",c("WFPS:","15 %", "30 %", "60 %", "90 %"), col=0:4,lty=1,bty="n")
legend("topleft",expression(paste("Temperature: 35", degree,"C")), bty="n")

plotIncunation(trt=c(35,15,20),ylim=c(0,1200), xlab="Incubation time (days)", ylab="")
linesIncunation(trt=c(35,30,20),col=2)
linesIncunation(trt=c(35,60,20),col=3)
linesIncunation(trt=c(35,90,20),col=4)
legend("topright",c("WFPS:","15 %", "30 %", "60 %", "90 %"), col=0:4,lty=1,bty="n")
legend("topleft",expression(paste("Temperature: 35", degree,"C")), bty="n")
par(mfrow=c(1,1))

clm=levels(IAll$SoilColumn) #Vector to identify soil columns by name

#Calculate cummulative respiration for the 35 day period for each column. First fits a spline and integrate area under the curve.
Resp=NULL
for(i in 1:length(clm)){
  set=subset(IAll,SoilColumn==clm[i])
  sp=splinefun(set$Day,set$CO2efflux)
  intg=integrate(sp,lower=1,upper=35)$value
  Ri=data.frame(Column=clm[i],Respiration=intg,Temperature=set[1,4],Moisture=set[1,5],Oxygen=set[1,6])
  Resp=rbind(Resp,Ri)
}
```

```{r}
# Figure 1
par(mar=c(4,4,1,0.1))
boxplot(Respiration~Temperature*Moisture*Oxygen,data=Resp, 
        ylab=expression(paste("Total respired C",O[2],"-C (", mu, "g)")),xlab="Treatment (Temperature-Moisture)",cex.axis=0.6,
        names=rep(c("25-15","35-15","25-30","35-30","25-60","35-60","25-90","35-90"),2))
abline(v=8.5,lty=3)
legend(2,1600, "Low oxygen (1%)", bty="n")
legend(10,1600, "High oxygen (20%)", bty="n")

# Comparison of treatment means (ANOVA)
summary(aov(lm(Respiration~Temperature*Moisture*Oxygen,data=Resp)))

#Other interesting plots not in publication
par(mfrow=c(2,2))
boxplot(Respiration~Moisture,data=Resp, 
        ylab="Total respiration",xlab=" ",cex.axis=0.5)

boxplot(Respiration~Temperature*Moisture,data=Resp, 
        ylab=" ",xlab=" ",cex.axis=0.5)

boxplot(Respiration~Moisture*Oxygen,data=Resp, 
        ylab="Total Respiration",xlab="Treatment",cex.axis=0.5)

boxplot(Respiration~Temperature*Oxygen,data=Resp, 
        ylab="",xlab="Treatment",cex.axis=0.5)
par(mfrow=c(1,1))
```

```{r include=FALSE}
###########################################################################################
# 2. Optimization for each treatment

# Calculation of initial C stocks
soilweight=450 #grams
TOC=c(0.04683975, 0.04703255, 0.04687287) #proportion of organic C in a gram of soil sample. Values from 3 replicates
C0=soilweight*mean(TOC) #in grams of carbon

#Function to fit two-pool parallel model to data
TwopOptm=function(Temperature,Moisture,Oxygen, Cconc=NULL,
                  inipars=c(k1=1/15,k2=1/100,gamma=0.1),met="Marq",
                  up=c(1.5,1,1),low=c(0,0,0)){
  
  days=seq(0,max(co2$Day)) #Incubation days
  Obs=data.frame(Day=seq(1,35,1),
                 CO2efflux=cumsum(spline(subst(Temperature,Moisture,Oxygen)[,1],(subst(Temperature,Moisture,Oxygen)[,2]*1e-06*10),xout=seq(1,35,1))$y),
                 sd=(spline(subst(Temperature,Moisture,Oxygen)[,1],cumsum(subst(Temperature,Moisture,Oxygen)[,2]*1e-06*10),xout=seq(1,35,1))$y))
  
  # Create a function that takes parameter values for a 2-pool model
  # and returns the accumulated release of C from respiration
  eCO2func=function(pars){
    mod=TwopParallelModel(
      t=days,
      ks=pars[1:2],
      gam=0,
      C0=Cconc*c(pars[3], 1-pars[3]), 
      In=0,
      pass=TRUE
    )
    Rt=getAccumulatedRelease(mod)
    return(data.frame(Day=days,CO2efflux=rowSums(Rt)))
  }
  
  # Create a cost function that takes the data and the parameters and calculates residuals
  eCO2cost=function(pars){
    modelOutput=eCO2func(pars)
    return(modCost(model=modelOutput, obs=Obs, err="sd",x="Day"))
  }
  
  # Run the optimization algorithm
  eCO2fit=modFit(f=eCO2cost,p=inipars,method=met,
                 upper=up,lower=low)
  
  #Best parameter set
  best.fit=eCO2fit$par
  print(best.fit)
  
  #Run the model again with best parameter set
  #fitmod=eCO2func(eCO2fit$par)
  fitmod=TwopParallelModel(t=days, ks=best.fit[1:2], 
                           gam=0,
                           C0=Cconc*c(best.fit[3], 1-best.fit[3]), 
                           In=0)
  fitCum=getAccumulatedRelease(fitmod)
  fitC=getC(fitmod)
  fitR=getReleaseFlux(fitmod)
  
  modelOut=as.data.frame(cbind(days,fitC,fitR,fitCum))
  names(modelOut)<-c("days","C1","C2","R1","R2","Rc1","Rc2")
  
  matplot(days, rowSums(fitCum), type="l",lty=1,xlab="Days", ylab="Respired C [g C day-1]",ylim=c(0,max(Obs[,2])))
  points(Obs[,1],Obs[,2])
  arrows(Obs[,1],Obs[,2]-Obs[,3],Obs[,1],Obs[,2]+Obs[,3],angle=90,
         length=0.1,code=3)
  legend("topright",c("Observations", "Predictions"),lty=1,bty="n")
  
  #Run a Bayesian optimization to estimate uncertainty ranges
  var0=eCO2fit$var_ms_unweighted
  
  eCO2mcmc=modMCMC(f=eCO2cost, p=eCO2fit$par, niter=10000, jump=NULL,  
                   var0=NULL, lower=low,
                   upper=up,burninlength = 1000)
  
  #Look at the output
  mcmc.summary=summary(eCO2mcmc)
  optim.summary=rbind(best.fit,mcmc.summary)
  rownames(optim.summary)[1]<-"best"
    
  pairs(eCO2mcmc)
  
  # Plot uncertainty in predictions
  predRange=sensRange(func=eCO2func, parInput=eCO2mcmc$par)
   
  plot(summary(predRange),xlab="Days",
       ylab=expression(paste("Respired C",O[2]," Efflux (g C ",d^-1, ")")),main="")
  points(Obs[,1:2])
  arrows(Obs[,1],Obs[,2]-Obs[,3],Obs[,1],Obs[,2]+Obs[,3],angle=90,
         length=0.1,code=3)

  return(list(optim.summary,TWO=c(Temperature,Moisture,Oxygen)))
}

set.seed(3) # for reproducility of results

### Run optimizations separately:
f251520=TwopOptm(Temperature = 25, Moisture = 15, Oxygen = 20, Cconc = C0,
                 inipars=c(k1=1/2,k2=1/10,gamma=0.5))

f25151=TwopOptm(Temperature = 25, Moisture = 15, Oxygen = 1, Cconc = C0,
                inipars=c(k1=1/2,k2=1/10,gamma=0.5))

f253020=TwopOptm(Temperature = 25, Moisture = 30, Oxygen = 20, Cconc = C0,
                 inipars=c(k1=1/2,k2=1/10000,gamma=0.00001))

f25301=TwopOptm(Temperature = 25, Moisture = 30, Oxygen = 1, Cconc = C0,
                inipars=c(k1=1/2,k2=1/10,gamma=0.5))

f256020=TwopOptm(Temperature = 25, Moisture = 60, Oxygen = 20, Cconc = C0,
                 inipars=c(k1=1/2,k2=1/10,gamma=0.5))

f25601=TwopOptm(Temperature = 25, Moisture = 60, Oxygen = 1, Cconc = C0,
                inipars=c(k1=0.2,k2=0.00001,gamma=0.5),up=c(0.3,0.001,1))

f259020=TwopOptm(Temperature = 25, Moisture = 90, Oxygen = 20, Cconc = C0,
                 inipars=c(k1=0.2,k2=1/10000,gamma=0.5),up=c(0.3,0.001,1))

f25901=TwopOptm(Temperature = 25, Moisture = 90, Oxygen = 1, Cconc = C0,
                inipars=c(k1=1/5,k2=1/10,gamma=0.5))

f351520=TwopOptm(Temperature = 35, Moisture = 15, Oxygen = 20, Cconc = C0,
                 inipars=c(k1=0.2,k2=1/10000,gamma=0.5),up=c(0.3,0.001,1))

f35151=TwopOptm(Temperature = 35, Moisture = 15, Oxygen = 1, Cconc = C0,
                inipars=c(k1=0.2,k2=1/10000,gamma=0.5),up=c(0.3,0.001,1))

f353020=TwopOptm(Temperature = 35, Moisture = 30, Oxygen = 20, Cconc = C0,
                 inipars=c(k1=1/2,k2=1/10,gamma=0.5))

f35301=TwopOptm(Temperature = 35, Moisture = 30, Oxygen = 1, Cconc = C0,
                inipars=c(k1=1/2,k2=1/10,gamma=0.5))

f356020=TwopOptm(Temperature = 35, Moisture = 60, Oxygen = 20, Cconc = C0,
                 inipars=c(k1=0.6,k2=1e-05,gamma=2e-04))

f35601=TwopOptm(Temperature = 35, Moisture = 60, Oxygen = 1, Cconc = C0,
                inipars=c(k1=1/2,k2=1/10,gamma=0.5))

f359020=TwopOptm(Temperature = 35, Moisture = 90, Oxygen = 20, Cconc = C0,
                 inipars=c(k1=1/2,k2=1/10,gamma=0.5))

f35901=TwopOptm(Temperature = 35, Moisture = 90, Oxygen = 1, Cconc = C0,
                inipars=c(k1=0.2,k2=1/10000,gamma=0.5),up=c(0.3,0.001,1))

## Prepare output for plotting
Ws=c(15,30,60,90) # Moisture range
pick=2 # 1: classical optimization, 2: bayesian optimization

k1T25=c(f251520[[1]][pick,1],f253020[[1]][pick,1],f256020[[1]][pick,1],f259020[[1]][pick,1])
k1T35=c(f351520[[1]][pick,1],f353020[[1]][pick,1],f356020[[1]][pick,1],f359020[[1]][pick,1])
k1T25O1=c(f25151[[1]][pick,1],f25301[[1]][pick,1],f25601[[1]][pick,1],f25901[[1]][pick,1])
k1T35O1=c(f35151[[1]][pick,1],f35301[[1]][pick,1],f35601[[1]][pick,1],f35901[[1]][pick,1])

k2T25=c(f251520[[1]][pick,2],f253020[[1]][pick,2],f256020[[1]][pick,2],f259020[[1]][pick,2])
k2T35=c(f351520[[1]][pick,2],f353020[[1]][pick,2],f356020[[1]][pick,2],f359020[[1]][pick,2])
k2T25O1=c(f25151[[1]][pick,2],f25301[[1]][pick,2],f25601[[1]][pick,2],f25901[[1]][pick,2])
k2T35O1=c(f35151[[1]][pick,2],f35301[[1]][pick,2],f35601[[1]][pick,2],f35901[[1]][pick,2])

gT25=c(f251520[[1]][pick,3],f253020[[1]][pick,3],f256020[[1]][pick,3],f259020[[1]][pick,3])
gT35=c(f351520[[1]][pick,3],f353020[[1]][pick,3],f356020[[1]][pick,3],f359020[[1]][pick,3])
gT25O1=c(f25151[[1]][pick,3],f25301[[1]][pick,3],f25601[[1]][pick,3],f25901[[1]][pick,3])
gT35O1=c(f35151[[1]][pick,3],f35301[[1]][pick,3],f35601[[1]][pick,3],f35901[[1]][pick,3])

#q25 -> low
k1T25l=c(f251520[[1]][6,1],f253020[[1]][6,1],f256020[[1]][6,1],f259020[[1]][6,1])
k1T35l=c(f351520[[1]][6,1],f353020[[1]][6,1],f356020[[1]][6,1],f359020[[1]][6,1])
k1T25O1l=c(f25151[[1]][6,1],f25301[[1]][6,1],f25601[[1]][6,1],f25901[[1]][6,1])
k1T35O1l=c(f35151[[1]][6,1],f35301[[1]][6,1],f35601[[1]][6,1],f35901[[1]][6,1])

k2T25l=c(f251520[[1]][6,2],f253020[[1]][6,2],f256020[[1]][6,2],f259020[[1]][6,2])
k2T35l=c(f351520[[1]][6,2],f353020[[1]][6,2],f356020[[1]][6,2],f359020[[1]][6,2])
k2T25O1l=c(f25151[[1]][6,2],f25301[[1]][6,2],f25601[[1]][6,2],f25901[[1]][6,2])
k2T35O1l=c(f35151[[1]][6,2],f35301[[1]][6,2],f35601[[1]][6,2],f35901[[1]][6,2])

gT25l=c(f251520[[1]][6,3],f253020[[1]][6,3],f256020[[1]][6,3],f259020[[1]][6,3])
gT35l=c(f351520[[1]][6,3],f353020[[1]][6,3],f356020[[1]][6,3],f359020[[1]][6,3])
gT25O1l=c(f25151[[1]][6,3],f25301[[1]][6,3],f25601[[1]][6,3],f25901[[1]][6,3])
gT35O1l=c(f35151[[1]][6,3],f35301[[1]][6,3],f35601[[1]][6,3],f35901[[1]][6,3])

#q75 -> up
k1T25u=c(f251520[[1]][8,1],f253020[[1]][8,1],f256020[[1]][8,1],f259020[[1]][8,1])
k1T35u=c(f351520[[1]][8,1],f353020[[1]][8,1],f356020[[1]][8,1],f359020[[1]][8,1])
k1T25O1u=c(f25151[[1]][8,1],f25301[[1]][8,1],f25601[[1]][8,1],f25901[[1]][8,1])
k1T35O1u=c(f35151[[1]][8,1],f35301[[1]][8,1],f35601[[1]][8,1],f35901[[1]][8,1])

k2T25u=c(f251520[[1]][8,2],f253020[[1]][8,2],f256020[[1]][8,2],f259020[[1]][8,2])
k2T35u=c(f351520[[1]][8,2],f353020[[1]][8,2],f356020[[1]][8,2],f359020[[1]][8,2])
k2T25O1u=c(f25151[[1]][8,2],f25301[[1]][8,2],f25601[[1]][8,2],f25901[[1]][8,2])
k2T35O1u=c(f35151[[1]][8,2],f35301[[1]][8,2],f35601[[1]][8,2],f35901[[1]][8,2])

gT25u=c(f251520[[1]][8,3],f253020[[1]][8,3],f256020[[1]][8,3],f259020[[1]][8,3])
gT35u=c(f351520[[1]][8,3],f353020[[1]][8,3],f356020[[1]][8,3],f359020[[1]][8,3])
gT25O1u=c(f25151[[1]][8,3],f25301[[1]][8,3],f25601[[1]][8,3],f25901[[1]][8,3])
gT35O1u=c(f35151[[1]][8,3],f35301[[1]][8,3],f35601[[1]][8,3],f35901[[1]][8,3])
```


```{r}
# Figure 2
par(mfrow=c(3,2),mar=c(2,4,2,0.5))
plot(Ws,k1T25,type="b",ylim=c(0,1.8), main="20% oxygen", xlab="",ylab=expression(k[1]))
lines(Ws,k1T35,type="b",col=2,pch=4)
arrows(Ws,k1T25l,Ws,k1T25u,angle=90,length=0.1,code=3)
arrows(Ws,k1T35l,Ws,k1T35u,angle=90,length=0.1,code=3,col=2)

plot(Ws,k1T25O1,type="b",ylim=c(0,1.8), main="1% oxygen", xlab="", ylab="")
lines(Ws,k1T35O1,type="b",col=2, pch=4)
arrows(Ws,k1T25O1l,Ws,k1T25O1u,angle=90,length=0.1,code=3)
arrows(Ws,k1T35O1l,Ws,k1T35O1u,angle=90,length=0.1,code=3,col=2)
legend("topright",c("25 Celcius","35 Celcius"),lty=1,col=1:2,pch=c(1,4),bty="n")

plot(Ws,k2T25,type="b",ylim=c(0,.00003), xlab="",ylab=expression(k[2]))
lines(Ws,k2T35,type="b",col=2, pch=4)
arrows(Ws,k2T25l,Ws,k2T25u,angle=90,length=0.1,code=3)
arrows(Ws,k2T35l,Ws,k2T35u,angle=90,length=0.1,code=3,col=2)

plot(Ws,k2T25O1,type="b",ylim=c(0,0.00003),xlab="",ylab="")
lines(Ws,k2T35O1,type="b",col=2, pch=4)
arrows(Ws,k2T25O1l,Ws,k2T25O1u,angle=90,length=0.1,code=3)
arrows(Ws,k2T35O1l,Ws,k2T35O1u,angle=90,length=0.1,code=3,col=2)

par(mar=c(4,4,1,0.5))
plot(Ws,gT25,type="b",ylim=c(0,0.001),ylab=expression(gamma),xlab="WFPS")
lines(Ws,gT35,type="b",col=2, pch=4)
arrows(Ws,gT25l,Ws,gT25u,angle=90,length=0.1,code=3)
arrows(Ws,gT35l,Ws,gT35u,angle=90,length=0.1,code=3,col=2)

plot(Ws,gT25O1,type="b",ylim=c(0,0.001),ylab="",xlab="WFPS")
lines(Ws,gT35O1,type="b",col=2, pch=4)
arrows(Ws,gT25O1l,Ws,gT25O1u,angle=90,length=0.1,code=3)
arrows(Ws,gT35O1l,Ws,gT35O1u,angle=90,length=0.1,code=3,col=2)
par(mfrow=c(1,1))

###########################################################################################
# 3. Optimization of all treatments simulteneously

#Create new objective function
objFunc<-function(pars,obs=co2){
  fT=fT.Q10(Temp=obs$Temperature, Q10=pars[2])
  fM=obs$Moisture/(pars[3]+obs$Moisture)
  fO=obs$Oxygen/(pars[4]+obs$Oxygen)
  
  Pred=C0*(pars[1]*(1-exp(-pars[5]*fT*fM*fO*obs$Day))+(1-pars[1])*(1-exp(-pars[6]*fT*fM*fO*obs$Day)))
  Obs=obs$CO2efflux
  Err=obs$sd
  Res=Pred-Obs
  res=Res/Err

  return(res)
}

#Classical optimization
inipars=c(gamma=0.5,Q10=1.4,K_M=20,K_O=20,k1=0.1,k2=0.0001)
best=modFit(f=objFunc,p=inipars,method="Pseudo",lower=c(0,0,0,0,0,0),upper=c(1,3,100,100,10,1))

#Bayesian optimization
fm=modMCMC(f=objFunc,p=c(coef(best)),var0=best$ms,niter=100000,burninlength = 2000,lower=c(0,0,1,0,0,0),upper=c(1,3,100,100,10,1))

# Run again with new initial values
fm=modMCMC(f=objFunc,p=c(fm$bestpar),var0=best$ms,niter=100000,burninlength = 2000,lower=c(0,0,1,0,0,0),upper=c(1,3,100,100,10,1))

plot(fm)

```

```{r}
#Figure 3
pairs(fm,pch=".",nsample=1000)

## Extract optimized parameters and plot sensitivities with uncertainties
Q10m=summary(fm)[1,2]
Ksm=summary(fm)[1,3]
Kom=summary(fm)[1,4]

Temp=seq(0,40,1)
W=seq(0,90,0.01)
O=seq(0,20,0.001)

dfT=function(Temp, Q10){fT.Q10(Temp=Temp, Q10=Q10)}
dfW=function(W, Ks){W/(Ks+W)}
dfO=function(O, Ko){O/(Ko+O)}

dfTdT=function(Temp,Q10){fT.Q10(Temp=Temp, Q10=Q10)*(1/10)}
dfWdW=function(W,Ks){Ks/((Ks+W)^2)}
dfOdO=function(O,Ko){Ko/((Ko+O)^2)}
```

```{r}
# Figure 4
par(mfrow=c(3,2), mar=c(5,4,1,1))
plot(Temp,dfT(Temp,Q10m),type="l", xlab="Temperature (Celcius)", ylab="f(T)",ylim=c(0,20),xlim=c(20,40),col=2)
polygon(x=c(Temp,rev(Temp)), y=c(dfT(Temp,summary(fm)[5,2]),rev(dfT(Temp,summary(fm)[7,2]))),col="gray",border=NA)
lines(Temp,dfT(Temp,Q10m),col=2)

plot(Temp,dfTdT(Temp,Q10m),type="l", xlab="Temperature (Celcius)", ylab=expression(paste(partialdiff,"f(T)","/",partialdiff,"T")),ylim=c(0,2),xlim=c(20,40),col=2)
polygon(x=c(Temp,rev(Temp)), y=c(dfTdT(Temp,summary(fm)[5,2]),rev(dfTdT(Temp,summary(fm)[7,2]))),col="gray",border=NA)
lines(Temp,dfTdT(Temp,Q10m),col=2)

plot(W,dfW(W,Ksm),type="l", xlab="Water-filled pore space (%)", ylab="f(W)",ylim=c(0,1),col=2)
polygon(x=c(W,rev(W)), y=c(dfW(W,summary(fm)[5,3]),rev(dfW(W,summary(fm)[7,3]))),col="gray",border=NA)
lines(W,dfW(W,Ksm),col=2)

plot(W,dfWdW(W,Ksm),type="l", xlab="Water-filled pore space (%)", ylab=expression(paste(partialdiff,"f(W)","/",partialdiff,"W")),ylim=c(0,0.05),col=2)
polygon(x=c(W,rev(W)), y=c(dfWdW(W,summary(fm)[5,3]),rev(dfWdW(W,summary(fm)[7,3]))),col="gray",border=NA)
lines(W,dfWdW(W,Ksm),col=2)

plot(O,dfO(O,Kom),type="l", xlab="Oxygen concentration (%)", ylab="f(O)",ylim=c(0,1),col=2)
polygon(x=c(O,rev(O)), y=c(dfO(O,summary(fm)[5,4]),rev(dfO(O,summary(fm)[7,4]))),col="gray",border=NA)
lines(O,dfO(O,Kom),col=2)

plot(O,dfOdO(O,Kom),type="l", xlab="Oxygen concentration (%)", ylab=expression(paste(partialdiff,"f(O)","/",partialdiff,"O")),ylim=c(0,0.1),col=2)
polygon(x=c(O,rev(O)), y=c(dfOdO(O,summary(fm)[5,4]),rev(dfOdO(O,summary(fm)[7,4]))),col="gray",border=NA)
lines(O,dfOdO(O,Kom),col=2)
par(mfrow=c(1,1))

par(mfrow=c(3,2), mar=c(5,4,1,1))
plot(c(25,35),dfT(c(25,35),Q10m),type="p", xlab="Temperature (Celcius)", ylab="f(T)",ylim=c(0,20),xlim=c(20,40),bty="n",pch=20)
arrows(x0=c(25,35),y0=dfT(c(25,35),quantile(fm$pars[,2],0.05)),x1=c(25,35),y1=dfT(c(25,35),quantile(fm$pars[,2],0.95)),angle=90,code=3,length=0.1)
lines(Temp,dfT(Temp,Q10m),lty=2)

plot(c(25,35),dfTdT(c(25,35),Q10m),type="p", xlab="Temperature (Celcius)", ylab=expression(paste(partialdiff,"f(T)","/",partialdiff,"T")),ylim=c(0,2),xlim=c(20,40),bty="n",pch=20)
arrows(x0=c(25,35),y0=dfTdT(c(25,35),quantile(fm$pars[,2],0.05)),x1=c(25,35),y1=dfTdT(c(25,35),quantile(fm$pars[,2],0.95)),angle=90,code=3,length=0.1)
lines(Temp,dfTdT(Temp,Q10m),lty=2)

plot(c(15,30,60,90),dfW(c(15,30,60,90),Ksm),type="p", xlab="Water-filled pore space (%)", ylab="f(W)",ylim=c(0,1),xlim=c(0,100),bty="n",pch=20)
arrows(x0=c(15,30,60,90),y0=dfW(c(15,30,60,90),quantile(fm$pars[,3],0.05)),x1=c(15,30,60,90),y1=dfW(c(15,30,60,90),quantile(fm$pars[,3],0.95)),angle=90,code=3,length=0.1)
lines(W,dfW(W,Ksm),lty=2)

plot(c(15,30,60,90),dfWdW(c(15,30,60,90),Ksm),type="p", xlab="Water-filled pore space (%)", ylab=expression(paste(partialdiff,"f(W)","/",partialdiff,"W")),ylim=c(0,0.02),xlim=c(0,100),bty="n",pch=20)
arrows(x0=c(15,30,60,90),y0=dfWdW(c(15,30,60,90),quantile(fm$pars[,3],0.05)),x1=c(15,30,60,90),y1=dfWdW(c(15,30,60,90),quantile(fm$pars[,3],0.95)),angle=90,code=3,length=0.1)
lines(W,dfWdW(W,Ksm),lty=2)

plot(c(1,20),dfO(c(1,20),Kom),type="p", xlab="Oxygen concentration (%)", ylab="f(O)",ylim=c(0,1),xlim=c(0,20),bty="n",pch=20)
arrows(x0=c(1,20),y0=dfO(c(1,20),quantile(fm$pars[,4],0.05)),x1=c(1,20),y1=dfO(c(1,20),quantile(fm$pars[,4],0.95)),angle=90,code=3,length=0.1)
lines(O,dfO(O,Kom),lty=2)

plot(c(1,20),dfOdO(c(1,20),Kom),type="p", xlab="Oxygen concentration (%)", ylab=expression(paste(partialdiff,"f(O)","/",partialdiff,"O")),ylim=c(0,0.1),xlim=c(0,20),bty="n",pch=20)
arrows(x0=c(1,20),y0=dfOdO(c(1,20),quantile(fm$pars[,4],0.05)),x1=c(1,20),y1=dfOdO(c(1,20),quantile(fm$pars[,4],0.95)),angle=90,code=3,length=0.1)
lines(O,dfOdO(O,Kom),lty=2)
par(mfrow=c(1,1))

xi=function(x){
  f1=dfT(x[1],Q10m)
  f2=dfW(x[2],Ksm)
  f3=dfO(x[3],Kom)
  f1*f2*f3
}

xiT=data.frame(treatments,xi(treatments))
names(xiT)[4]<-"xi"

plot(subset(xiT,Temperature==25 & Oxygen==20,select=c(Moisture,xi)),col=4,ylim=c(0,3),pch=19,ylab=expression(paste(xi, " (unitless)")),xlab="Water filled pore space (%)",type="b")
lines(subset(xiT,Temperature==35 & Oxygen==20,select=c(Moisture,xi)),col=2,pch=19,type="b")
lines(subset(xiT,Temperature==25 & Oxygen==1,select=c(Moisture,xi)),col=4,pch=4,type="b")
lines(subset(xiT,Temperature==35 & Oxygen==1,select=c(Moisture,xi)),col=2,pch=4,type="b")
abline(h=1,lty=2)
legend("topleft",c("T = 25 C, O = 20 %", "T = 35 C, O = 20%", "T = 25 C, O = 1%", "T = 35 C, O = 1%"), lty=1, col=c(4,2),pch=c(19,19,4,4),bty="n")

###########################################################################################
#End
```


